% !TeX encoding = UTF-8
% !TeX root = MAIN.tex


{%
	\selectlanguage{english}
	\chapter*{}

\textit{
I would like to express my gratitude to Dr. Jochen Güntner, Professor of Macroeconomics at Johannes Kepler University Linz, for providing me with the opportunity to write this bachelor's thesis in a field I haven't been exposed to academically beyond introductory level courses. \\
I appreciate his valuable comments on the original version of my submitted bachelor thesis.\\ \\
I also want to take this opportunity to mention Dr. Helga Wagner from the Institute of Applied Statistics, Dr. Martina Zweimüller, Dr. Matthias Fahn from the Department of Economics, and Dr. Florin Ciucu from the Computer Science Department at the University of Warwick. Their courses in Time Series Analysis, Intermediate Econometrics, Behavioural Economics, and Data Analytics have had the most significant influence on my current understanding in the field of Economics.
}

\newpage

\section*{Declaration of Academic Honesty}


Hereby, I declare that I have composed the presented paper independently on my own
and without any other resources than the ones indicated. All thoughts taken directly or
indirectly from external sources are properly denoted as such.
This bachelor thesis has neither been previously submitted to another authority.\\
\\ \\ \\ \\ 
(Reichel F.)


%This page is left blank intently.

%\textit{
%In European stock markets, patterns unfold,\\
%Empirical evidence, a tale yet untold.\\
%Excess profits, a phenomenon profound,\\
%Before ECB decisions, they can be found.}
%\\ \\
%\textit{
%Monetary policy, a force to reckon,\\
%In the realm of finance, it's a lesson.\\
%Academia's words, they guide our way,\\
%Unveiling truths, where numbers sway.}
%\\ \\
%\textit{
%Economics and finance, intertwined,\\
%A dance of numbers, a rhythm defined.\\
%So let us delve into this intricate sphere,\\
%Where markets and policies, forever adhere.}
%\\ \\
%\\ \\
%- A Poem written by generative AI using OpenAI's gpt-3.5-turbo-Model (2023)
%}

% Wird vermutl. nicht benoetigt.
%{%
%	\selectlanguage{naustrian}
%	\chapter*{Kurzfassung}
%	
%	Kurzfassung auf Deutsch. 
%}
%
%{%
%	\selectlanguage{english}
%	\chapter*{Abstract}
%	
%	Abstract
%}