% !TeX encoding = UTF-8
% !TeX root = MAIN.tex

\chapter{Motivation}

The starting point of this thesis is recently conducted research that studies the link and possible causal effects between monetary policy decisions by the FED and the stock market in the U.S., not only in an ex-post but also in an ex-ante sense.

The paper Stock Returns over the FOMC Cycle \parencite{cieslak_stock_2019} finds a pattern in financial markets around the world that suggests that stock market excess returns in the last 23 were entirely earned in even weeks (0, 2, 4 and 6) starting from the last FOMC meeting. The authors tie their findings to a known phenomenon called "Fed Put", by which they mean accommodating monetary policy.

In a follow-up paper, The Economics of the FED Put \parencite{cieslak_economics_2021} the authors use textual analysis of FOMC (Federal Open Market Commitee) scripts to identify and measure the causal effect that policymakers indeed pay intention to the stock market, especially since the mid-1990s and stock market performance is linked with the FED’s internal growth projections. The authors further claim that even if the policymakers seem to be aware that a dynamic like the FED put could induce risk-taking behavior leading to moral-hazard implications, it does not particularly affect their decision-making in an ex-ante sense.

In my thesis, I aim to find out whether the financial pattern regarding stock excess returns in FOMC even weeks is still relevant from 2016 (which should not be the case, especially once the information has reached the market) onwards (probably complicated by the COVID-19 crisis) since the paper published in 2019 only investigates this pattern before 2016. Additionally, the authors prove the relevance of their financial pattern worldwide using exchange-traded funds (ETFs) containing European stocks. I want to include further results with a specific focus on European stock returns.

%In my thesis I aim to find out whether the "FED Put" remains relevant in the %Eurozone from 2016 onwards till 2023  and whether a similar dynamic can %be observed within the European Central Bank's policy, particularly concerning interest rates and Exchange-Traded Funds (ETFs) containing %European stocks. 

\input{chapter1.tex}

\input{chapter2.tex}

%\input{chapter3.tex}

\chapter{Conclusion}

tbd.

\chapter{Appendix}

\section{R Code}
\subsection{FOMC Cycle Dummy Generation}
\label{app:fomc_code}

The R code in this section, provided in Listing~\ref{lst:fomc_code}, generates FOMC week dummy variables based on the defined FOMC cycle patterns. The resulting data frame is then saved to a CSV file.

\lstinputlisting[caption={R code for FOMC Week Dummy Generation}, label={lst:fomc_code}]{../FOMC_dummy_generation/generate_fomc_cycle_dummies.R}

\subsection{CSV File of generated FOMC dummies}
\label{app:first_35_lines_csv}

The listing~\ref{lst:first_35_lines_csv} displays the first 35 examples of the generated FOMC dummies in the CSV file,  containing approximately one FOMC cycle consisting of 7 work-weeks:

\lstinputlisting[firstline=2, lastline=36, caption={First 35 examples of the generated FOMC dummies}, label={lst:first_35_lines_csv}, prebreak=\mbox{$\hookrightarrow$}]{../FOMC_dummy_generation/fomc_week_dummies_1994_nov2023.csv}

\section{STATA Code}
\subsection{Measurement and Estimation Analysis}
\label{app:stata_code}

The STATA code in this section, provided in Listing~\ref{lst:stata_code}, involves the use of \texttt{estab} commands to measure and estimate stock returns over the FOMC cycle. It includes functions to reload data, calculate stock excess returns, and generate graphs for analysis.

\lstinputlisting[caption={STATA code for Measurement and Estimation Analysis}, label={lst:stata_code}]{../stock_returns_over_the_fomc_cycle_revisited.do}


